Ethereum: Un Registro Generico delle Transazioni Sicuro e Decentralizzato \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-02-17 Paper.tex
Update Paper.tex

Fees (denominated in gas) are charged under three distinct circumstances, all three as prerequisite to the execution of an operation. The first and most common is the fee intrinsic to the computation of the operation (see Appendix \ref{app:fees}). Secondly, gas may be deducted in order to form the payment for a subordinate message call or contract creation; this forms part of the payment for {\small CREATE}, {\small CALL} and {\small CALLCODE}. Finally, gas may be paid due to an increase in the usage of the memory.

Over an account's execution, the total fee for memory-usage payable is proportional to smallest multiple of 32 bytes that are required such that all memory indices (whether for read or write) are included in the range. This is paid for on a just-in-time basis; as such, referencing an area of memory at least 32 bytes greater than any previously indexed memory will certainly result in an additional memory usage fee. Due to this fee it is highly unlikely addresses will ever go above 32-bit bounds. That said, implementations must be able to manage this eventuality.

>>>>

Le commissioni (denominate in gas) sono dovute in tre distinte circostanze, tutte e tre come prerequisito all'esecuzione di un'operazione. La prima e più comune è la fee inrinseca alla computazione di un'operazione (si veda Appendix \ref{app:fees}). Secondariamente,  il gas può essere dedotto con il fine di eseguire il pagamente un messaggio di chiamata subotdinato o la creazione di un contratto; questo fa parte del pagamento per {\small CREATE}, {\small CALL} and {\small CALLCODE}. Infine, il gas può essere pagato a causa di un incremento nell'uso della memoria.

Nel corso dell'esecuzione di un account, la commissione totale esigibile per l'uso della memoria è proporzionale al più piccolo multiplo di 32 byte che sono richiesti in modo tale che tutti gli indici della memoria (sia per leggere o scrivere) sono incluesi nel range. Questo viene pagato in modo tempestivo; as such, referencing an area of memory at least 32 bytes greater than any previously indexed memory will certainly result in an additional memory usage fee. Due to this fee it is highly unlikely addresses will ever go above 32-bit bounds. That said, implementations must be able to manage this eventuality.
